\section{Examples} \label{examples}

The TEST\_DATA directory contains some examples of the application of the network\_synthesis process. These examples consist of impedance functions which may be in rational function form (as produced by GGI\_TLM\_filter\_fit 
from the GGI\_TLM project (https://github.com/ggiemr/GGI\_TLM)) or alternatively
in pole-residue form as produced by the Vector\_fit process (https://github.com/chrissmartt/vector\_fit)

The script run\_test runs the network synthesis process. The argument of run\_test is the filename for 
the test data. The script runs the network synthesis process and produces a circuit file (ngspice\_circuit.cir)
suitable for running in ngspice. The script runs ngspice and the output of the ngspice circuit gives the frequeny domain voltage due to 
a unit current source and hence gives the (complex) impedance. 

A process 'compare\_results' provides a measure of the difference between the complex spice model impedance and the
impedance calculated by evaluating the input rational function or pole-zero impedance function. 
Gnuplot then plots the comparison between the evaluation of the input function and the ngspice result. 

Examples:

1. Rational function describing the impedance of a ladder network with R in series with a parallel combination
of a C branch and a RL branch.

run\_test test\_RCRL\_ladder

2. Rational function fit to measured impedance data. 
The filter fit was produced by GGI\_TLM\_filter\_fit from the GGI\_TLM project (https://github.com/ggiemr/GGI\_TLM)

run\_test test\_GGI\_TLM\_filter\_fit\_Z

3. Pole-zero representation of a real capacitor generated by the VECTOR\_FIT software (https://github.com/chrissmartt/vector\_fit)
from measured data

run\_test test\_Vfit.filter




\clearpage
